\documentclass{résumé} 
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} 
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{DENIS MURPHY}
\address{Co. Kerry, Ireland} 
\address{https://github.com/denismurphy \\ denismurphy\char"0040me.com}
\begin{document}

\begin{rSection}{Overview}
\normalfont Experienced software engineer in various languages and platforms, passionate about learning new technologies. Proven track record of delivering reliable software and taking on new challenges. \\
\end{rSection}

\begin{rSection}{Work Experience}
\begin{rSubsection}{Dairymaster, Co. Kerry}{May 2016 - Current}{Software Engineer}{}
 \item \normalfont Main responsibilities include conducting analysis, designing solutions, selecting technologies, and implementing frameworks across Software team.
 \item \normalfont DM LiveVue, bespoke touchscreen application that acts as a mission control for farmers in milking parlours and runs on ruggedized industrial touch screen.
 \item \normalfont SwiftCool, backend api's, web frontend and iOS application designed to remotely control and monitor a fleet of CoolControl milk tanks via MQTT.
 \item \normalfont DataSync, a system that performs bi-directional data synchronization from the farm edge to the cloud.
 \item \normalfont DairyVue 360 iOS mobile application.
 \item \normalfont Performing blue teaming activities on our cloud infrastructure in AWS.
\end{rSubsection}

Tech Stack: \normalfont EKS, ECS, Kubernetes, Docker, EC2, DynamoDB, SQS, S3, MySQL, Redis, \\ .Net Core/.Net 7, .Net Identity, Swift, SwiftUI, Objective-C, UIKit, TypeScript, AngularJS, \\Angular, Bootstrap, MQTT, Protocol Buffer, Java, Kotlin, Linux \\

\begin{rSubsection}{Quest Computing, Dublin}{\textbf{November 2012 – May 2016}}{\textbf{Software Engineer}}{}
 \item \normalfont Worked on-site in HSE PCRS main responsible for monitoring and maintaining large public sector production environment supporting our health service running in a government data center and participated in all stages of development, with a focus on analysis, design, technology selection, and framework design/implementation.
 \item \normalfont Migrating legacy Apache Structs, JavaEE systems to Spring Boot.
 \item \normalfont Refactored large PL/SQL packages into modern api's following a service-oriented architecture.
 \item \normalfont Automating, monitoring, and performing blue teaming activities on our government data center infrastructure.
\end{rSubsection}

\textbf{Tech Stack:} \normalfont Spring Boot, Spring Security, Oracle, SOA, Maven, Java 8, .Net, WPF, XAML, WCF, Ribbon UI, Entities Framework, SQL Server\\

\begin{rSubsection}{UTS Insearch, Sydney}{\textbf{April 2015 – January 2016}}{\textbf{Independent Contractor}}{}
 \item \normalfont Design and development of a mobile-first website aimed at the Chinese-speaking market in China, Taiwan, and Hong Kong.
\end{rSubsection}

\textbf{Tech Stack:} \normalfont S3, CloudFront, Bootstrap, Mobile First, Responsive Design
\pagebreak

\begin{rSubsection}{BSB (Business Solutions Builders), Dublin}{\textbf{January 2011 – August 2012}}{\textbf{Junior Software Engineer}}{}
 \item \normalfont Member of the Soliam Team worked on adding new functionality to Back Office, Front Office, and in-house data warehouse. Developed solutions for clients such as AXA, BNP Paribas, Societe Generale, and Ethias. Also worked on refactoring older parts of Soliam, bug fixes, and unit testing.
\end{rSubsection}

\textbf{Tech Stack:} \normalfont Adobe Flex, BlazeDS, PL/SQL, JBoss, Maven, BDUF, JIRA, ETL, Oracle Datawarehouse, Struts, IBM RAD, Oracle, EJB, CORBA , RMI \\

\begin{rSubsection}{Microsoft, Dublin}{\textbf{March 2010 – May 2010}}{\textbf{Work Experence}}{}
 \item \normalfont Intern in Sales, Marketing, and Services Group (SMSG) for EMEA. Duties included attending Microsoft conferences in Dublin, promoting Microsoft technologies on college campuses, and receiving internal training on Microsoft stack including Azure, .Net and Team Foundation Server.
\end{rSubsection}

\begin{rSubsection}{Microsystems, Chicago, IL}{\textbf{May 2007 - November 2007}}{\textbf{Intern}}{}
 \item \normalfont Intern on a J1 visa, I worked on DocXtools and D3, focusing on converting Microsoft Office Documents to the Microsoft Open XML document format and then reverse engineering XML for these documents. I created XSLT templates that could be used later for parsing the documents. At the end of my internship, I handed over my work to a Senior Software Engineer..
\end{rSubsection}

\textbf{Tech Stack:} \normalfont C\char"0023, NUnit, TFS, XMLSpy \\

\begin{rSection}{Education and Certification}
{\bf Apple Development with Swift} \hfill {\em Nov 2022 – Jan 2023} 
\\ \normalfont Swift, iOS, App Development, UIKit

{\bf AWS Certified Solutions Architect} \hfill {\em \textbf{June 2022 – Dec 2022}} 
\\ \normalfont Fundamentals, Architecture, Security, Networking, Cost-Optimised

{\bf Certified Information Systems Security Professional} \hfill {\em \textbf{Jan 2021 – Oct 2021}} 
\\ \normalfont ISC2, Security, Monitoring, Analysis, Audit, Architecture

{\bf Certified Kubernetes Application Developer} \hfill {\em \textbf{Jun 2020 – Sep 2020}} 
\\ \normalfont Kubernetes, Containers, Scaling, Architecture

{\bf MongoDB for Java Developers} \hfill {\em \textbf{Oct 2013 – Dec 2013}} 
\\ \normalfont MongoDB, Document-Oriented Database, JSON, BSON

{\bf Functional Programming in Scala} \hfill {\em \textbf{Sep 2013 – Nov 2013}} 
\\ \normalfont Functional Programming, Pattern Matching, Lazy Evaluation, Sbt

{\bf SpringSource Certified Spring Professional} \hfill {\em \textbf{Jan 2013 – Jul 2013}} 
\\ \normalfont Spring Boot, Spring MVC, Spring Security, Spring Data

{\bf Oracle Certified Professional Java Programmer (SCJP)} \hfill {\em \textbf{Oct 2010 – Jan 2011}} 
\\ \normalfont Java, JavaEE

{\bf BSc (Hons) in Computing with Multimedia} \hfill {\em \textbf{Sep 2005 – Jun 2010}} 
\\ \normalfont Algorithms, Design Patterns, Data Structures, OOAD,
Compilers

{\bf FETAC Level 6 Certificate in Interactive Multimedia.} \hfill {\em \textbf{May 2002 – May 2003}} 
\\ \normalfont Interactive Design, Illustration
\end{rSection}
\pagebreak

\begin{rSection}{REFEREES}
\item Edmond Harty: \normalfont Vice-President Engineers Ireland, Adjunct Full Professor UCD
\item \bf Adrian Hynes: \normalfont Director Cloud Engineering at Fidelity Investments
\item \bf Tom O'Sullivan: \normalfont CEO of Microsystems, Chicago, IL
\item \bf Ed Sheldon: \normalfont Lecturer in Computer Science at Munster Technological University
\item \normalfont References available upon request.

\end{rSection}
\end{rSection}

\end{document}
